\textit{Supplementary materials for}: Text embedding models yield high-resolution insights into conceptual knowledge from short multiple-choice quizzes

### 2023-02-01 paper/main.tex

\begin{equation}
    \mathrm{ncorr}(x, y) = \frac{\mathrm{corr}(x, y) - \mathrm{mincorr}}{\mathrm{maxcorr} - \mathrm{mincorr}},
\end{equation}
and where $\mathrm{mincorr}$ and $\mathrm{maxcorr}$ are the minimum and maximum
correlations between any lecture timepoint and question, taken over all
timepoints in the given lecture, and all five questions \textbf{about} that lecture appearing on the given quiz. 
We also define $f(s, \Omega)$ as the
$s$\textsuperscript{th} topic vector from the set of topic vectors $\Omega$.
Here $t$ indexes the set of lecture topic vectors, $L$, and $i$ and $j$ index
the topic vectors of questions used to estimate the knowledge trace, $Q$. Note
that ``correct'' denotes the set of indices of the questions the participant
answered correctly on the given quiz.

>>>>

\begin{equation}
    \mathrm{ncorr}(x, y) = \frac{\mathrm{corr}(x, y) - \mathrm{mincorr}}{\mathrm{maxcorr} - \mathrm{mincorr}},
\end{equation}
and where $\mathrm{mincorr}$ and $\mathrm{maxcorr}$ are the minimum and maximum
correlations between any lecture timepoint and question, taken over all
timepoints in the given lecture, and all five questions \textit{about} that lecture appearing on the given quiz. 
We also define $f(s, \Omega)$ as the
$s$\textsuperscript{th} topic vector from the set of topic vectors $\Omega$.
Here $t$ indexes the set of lecture topic vectors, $L$, and $i$ and $j$ index
the topic vectors of questions used to estimate the knowledge trace, $Q$. Note
that ``correct'' denotes the set of indices of the questions the participant
answered correctly on the given quiz.

### 2023-02-01 paper/supplement.tex

\newcommand{\knowledgeMaps}{5}

\title{\textit{Supplementary materials for}: Text embedding models yield high
resolution insights into conceptual knowledge from short multiple choice
quizzes}

@@

\newcommand{\topics}{3}

@@

\caption{\textbf{Topics.} The table displays the 10 top-weighted word from
    each of the 15 topics identified from sliding windows of two course video
    transcripts (see \textit{Constructing text embeddings of multiple videos
    and questions}).}
    \label{tab:topics}
\end{table}

@@

\caption{\textbf{Topic weights. A. Average topic weights for each lecture and
question type}. The bar plots display each topic's average weight across
lecture timepoints (top row) and questions (bottom row); colors denote topics.
The top-weighted words from the highest-weighted topic from each lecture are
displayed in the upper right (orange: topic 2; yellow-green: topic 4). The
top-weighted words from the full set of topics may be found in
Table~\ref{tab:topics}. \textbf{B. Relationships between average topic
weights.} Pairwise correlations between the distributions of average topic
weights for each lecture and question category. Each row and column corresponds
to a bar plot in Panel A. Also see Figure~\topics A in the main text.}

@@

    \caption{\textbf{Individual participants' knowledge maps estimated from
    Quiz 1 responses.} Each panel is in the same format as the knowledge maps
    displayed in the left panel of Figure~\knowledgeMaps A in the main text,
    but here the maps have been computed separately for each participant.}

@@

    \caption{\textbf{Individual participants' knowledge maps estimated from
    Quiz 2 responses.} Each panel is in the same format as the knowledge maps
    displayed in the middle panel of Figure~\knowledgeMaps A in the main text,
    but here the maps have been computed separately for each participant.}

@@

    \caption{\textbf{Individual participants' knowledge maps estimated from
    Quiz 3 responses.} Each panel is in the same format as the knowledge maps
    displayed in the right panel of Figure~\knowledgeMaps A in the main text,
    but here the maps have been computed separately for each participant.}

@@

    \caption{\textbf{Individual participants' learning maps estimated from
    Quiz 1 and 2 responses.} Each panel is in the same format as the learning map
    displayed in the left panel of Figure~\knowledgeMaps B in the main text,
    but here the maps have been computed separately for each participant.}

>>>>

\newcommand{\topics}{3}
\newcommand{\knowledgeMaps}{7}

\title{\textit{Supplementary materials for}: Text embedding models yield 
high-resolution insights into conceptual knowledge from short multiple-choice
quizzes}

@@

@@

\caption{\textbf{Topics.} The table displays the 10 top-weighted words (columns) from
    each of the 15 topics (rows) identified from sliding windows of the two course video
    transcripts (see \textit{Constructing text embeddings of multiple lectures
    and questions}).}
    \label{tab:topics}
\end{table}

@@

\caption{\textbf{Topic weights. A. Average topic weights for each lecture and
question set}. The bar plots display each topic's average weight across
lecture timepoints (top row) and questions (bottom row); colors denote topics.
The top-weighted words from the highest-weighted topic from each lecture are
displayed in the upper right (orange: topic 2; yellow-green: topic 4). The
top-weighted words from the full set of topics may be found in
Table~\ref{tab:topics}. \textbf{B. Relationships between average topic
weights.} Pairwise correlations between the distributions of average topic
weights for each lecture and question set. Each row and column corresponds
to a bar plot in Panel A. Also see Figure~\topics~in the main text.}

@@

    \caption{\textbf{Individual participants' knowledge maps estimated from
    Quiz 1 responses.} Each panel is in the same format as the knowledge map
    displayed in the left panel of Figure~\knowledgeMaps A in the main text,
    but here the maps are shown separately for each participant.}

@@

    \caption{\textbf{Individual participants' knowledge maps estimated from
    Quiz 2 responses.} Each panel is in the same format as the knowledge map
    displayed in the middle panel of Figure~\knowledgeMaps A in the main text,
    but here the maps are shown separately for each participant.}

@@

    \caption{\textbf{Individual participants' knowledge maps estimated from
    Quiz 3 responses.} Each panel is in the same format as the knowledge map
    displayed in the right panel of Figure~\knowledgeMaps A in the main text,
    but here the maps are shown separately for each participant.}

@@

    \caption{\textbf{Individual participants' learning maps estimated from
    Quiz 1 and 2 responses.} Each panel is in the same format as the learning map
    displayed in the left panel of Figure~\knowledgeMaps B in the main text,
    but here the maps are shown separately for each participant.}
